\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2015-11-12 doc/USER_MANUAL/01_introduction.tex
added a sentence about varying density in fluids to the users manual

@@

The SEM was originally developed in computational fluid dynamics \citep{Pat84,MaPa89}
and has been successfully adapted to address problems in seismic wave
propagation. Early seismic wave propagation applications of the SEM,
utilizing Legendre basis functions and a perfectly diagonal mass matrix,
include \citet{CoJoTo93}, \citet{Kom97}, \citet{FaMaPaQu97}, \citet{CaGa97},
\citet{KoVi98} and \citet{KoTr99}, whereas applications involving
Chebyshev basis functions and a nondiagonal mass matrix include \citet{SePr94},
\citet{PrCaSe94} and \citet{SePrPr95}.\\

>>>>

\red{In fluids, when gravity is turned off, SPECFEM2D uses the classical
linearized Euler equation; thus if you have sharp local variations of
density in the fluid (highly heterogeneous fluids
in terms of density) or if density becomes extremely small in some
regions of your model (e.g. for upper-atmosphere studies), before using
the code please make sure the linearized Euler equation is a valid
approximation in the case you want to study, and/or if you should turn gravity on.
For more details on that see e.g. \cite{COA2011}.}\\

@@

The SEM was originally developed in computational fluid dynamics \citep{Pat84,MaPa89}
and has been successfully adapted to address problems in seismic wave
propagation. Early seismic wave propagation applications of the SEM,
utilizing Legendre basis functions and a perfectly diagonal mass matrix,
include \citet{CoJoTo93}, \citet{Kom97}, \citet{FaMaPaQu97}, \citet{CaGa97},
\citet{KoVi98} and \citet{KoTr99}, whereas applications involving
Chebyshev basis functions and a non-diagonal mass matrix include \citet{SePr94},
\citet{PrCaSe94} and \citet{SePrPr95}.\\
